What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-02-02 text/01_CogSci_abstract/paper.tex
few typos

\author{{\large \bf Michael Franke, Fabian Dablander, Anthea Sch\"{o}ller} \\
  \{michael.franke, fabian.dablander, anthea.schoeller\}@uni-tuebingen.de \\
  Department of Linguistics, Wilhelmstra\ss e 19 \\
  72074 T\"{u}bingen, Germany \AND
  {\large \bf Erin Bennett, Judith Degen, Michael Henry Tessler, Justine Kao, Ciyang Qing, Noah D. Goodman}\\
  \{ebennett, jdegen, mtessler, justinek, qciyang, ngoodman\}@stanford.edu \\
  Department of Psychology, Stanford University \\
  450 Serra Mall, Stanford, CA 94305 USA }

@@

%
In sum, there is tradeoff between simplicity of paradigms and their information
content. Ideally, we would like to have an experimental method for measuring subjective beliefs
that (i) provides sufficient and reliable-enough information about subjective beliefs to derive
testable predictions from cognitive models that rely on such information, (ii) is easy to
understand by participants, (iii) is easy to implement, and that (iv) does not require
sophisticated means of data analysis. Moreover, the ideal method would be (v) flexible enough
to allow inferred subjective belief distributions beyond standard parameterized distributions
and (vi) would provide a good approximation of the central tendency or average of subjective
beliefs in a given population. The latter would allow using one set of participants for
measuring prior beliefs and another for whatever other task is of interest, so as to avoid
potential cross-over effects.

@@

Finally, another aspect that our model has ignored so far are potential individual differences
in the way subjective beliefs $P_{ij}$ generates responses. It is not unlikely that there is
individual variation in at least some link function parameters, such as $\kappa$, which
expresses end-point attraction or end-point aversion in the binned histograms task. A detailed
investigation of such individual-level differences must be left to future work. Still, we
believe that the model presented here is an important first step towards finding reliable and
practical means of measuring what the crowd believes.

>>>>

\author{{\large \bf Michael Franke, Fabian Dablander, Anthea Sch\"{o}ller} \\
  \{michael.franke, fabian.dablander, anthea.schoeller\}@uni-tuebingen.de \\
  Department of Linguistics, Wilhelmstra\ss e 19 \\
  72074 T\"{u}bingen, Germany \AND
  {\large \bf Erin Bennett, Judith Degen, Michael Henry Tessler, Justine Kao, Noah D. Goodman}\\
  \{ebennett, jdegen, mtessler, justinek, ngoodman\}@stanford.edu \\
  Department of Psychology, Stanford University \\
  450 Serra Mall, Stanford, CA 94305 USA }

@@

%
In sum, there is a tradeoff between simplicity of paradigms and their information
content. Ideally, we would like to have an experimental method for measuring subjective beliefs
that (i) provides sufficient and reliable-enough information about subjective beliefs to derive
testable predictions from cognitive models that rely on such information, (ii) is easy to
understand by participants, (iii) is easy to implement, and that (iv) does not require
sophisticated means of data analysis. Moreover, the ideal method would be (v) flexible enough
to allow inferred subjective belief distributions beyond standard parameterized distributions
and (vi) would provide a good approximation of the central tendency or average of subjective
beliefs in a given population. The latter would allow using one set of participants for
measuring prior beliefs and another for whatever other task is of interest, so as to avoid
potential cross-over effects.

@@

Finally, another aspect that our model has ignored so far are potential individual differences
in the way subjective beliefs $P_{ij}$ generate responses. It is not unlikely that there is
individual variation in at least some link function parameters, such as $\kappa$, which
expresses end-point attraction or end-point aversion in the binned histograms task. A detailed
investigation of such individual-level differences must be left to future work. Still, we
believe that the model presented here is an important first step towards finding reliable and
practical means of measuring what the crowd believes.
